Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-09 proposal/proposal.tex

% Not sure how to cite this; can someone help?
\bibitem{parkingWiki}  ACMx ``Parking Sensor Wiki'' https://github.com/ColoradoSchoolOfMines/parking\_sensor/wiki

>>>>

\bibitem{parkingWiki}  ACMx ``Parking Sensor Wiki'' \begin{verbatim}https://github.com/ColoradoSchoolOfMines/parking_sensor/wiki\end{verbatim} % Not sure how to cite this; can someone help?
